New lower bounds for Schur and weak Schur numbers

### 2021-04-06 article/article.tex
redaction sat

\subsection{Search space previously used in computer search for lower bound may not contain the optimal partitions}

>>>>

We then encode the existence of a partition of \([\![1,n]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer 
\(i \in [\![1,n]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\). 
The corresponding clauses are:

\begin{itemize}
\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,n]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c 
\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
\item \textbf{union:} \(\forall i \in [\![1,n]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
\item \textbf{disjoint:} \(\forall i \in [\![1,n]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
\end{itemize}

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by 
enforcing that \(m_1 < ... < m_k\). The correspond clauses are: \linebreak
\textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

\subsection{The search space previously used in computer search for lower bound may not contain the optimal partitions}
